---
title: "Stat291_Project-1"
output:
  pdf_document: default
  html_document:
    df_print: paged
  word_document: default
  html_notebook: default
---
Dumbledore's army:

- 2429066 Mert Göksel 
- 2290658 Rümeysa Durdağ 
- 2361160 Merve Çakır 


1-)

The data is about daily coronavirus readings, it has 5 columns. 
This columns are firstly date, then comes the province of the country, the country, 
latitude/longitude, the type of the case (cases/deaths/recovered) 
and finally the number of those cases.

```{r}
library(coronavirus) #CORONAVIRUS DATA

data <- coronavirus #assign the dataset to a variable

head(data) #first 6 rows of the data
```

2-)
```{r}
sapply(data, class)
```
3-) Created questions about the dataset:

3.1-) What is the index of the max case number for any type?
```{r}
which.max(data$cases)
data[106531,]
```

3.2-) What rows are for United states?
```{r}
c(min(which(data$country == "US")), max(which(data$country == "US")))
```

4.1-) Is there any NA value?

```{r}
any(is.na(data)) 
```

Our dataframe doesnt contain any NA values but if it did then we would have shown it as

```{r}
which(is.na(data))
```

4.2-) Print the col names

```{r}
names(data)
```

If there was no names assigned we would have assigned them with

colnames(data) <- c(names) #c(names) = names we gave in order

4.3-) Show first 20 rows of our data:

```{r}
head(data, 20)
```

4.4-) The numeric values are latitude/longitude and cases

```{r}
c(mean(data$lat), mean(data$long), mean(data$cases))
```

The table of country&cases can be made with the code below but as there are too many countries in the dataset we wont run it on our pdf
```{r echo = T, results = 'hide'}
table(data$country, data$cases) 
```

#4.5-) Order your data depending on one of the numeric variables.

```{r}
data_ordered <- data[order(data$cases),]
head(data_ordered)
#this is too long as well so we printed the head of the dataset.
```

5.1-) Create a new variable which is a linear combination
Our numeric variables will be: v1 = latitude, v2 = longitude
Our formula for linear combination will be = 5v1-4v2
```{r}
v1 <- data$lat
v2 <- data$long
dumbeldors_army <- 5*v1-4*v2
data$dumbeldors_army <- dumbeldors_army
head(data)
```

5.2-) By using for loops, multiply one of your numeric variables with another one
We took the lat, long var for v1&v2 but they are too repetitive as each country has many lines of data but their lat&long doesnt change. So we will take only the unique values
```{r echo = T, results = 'hide'}
v1_unique = unique(v1)
v2_unique = unique(v2)

multiply_list <- list()
for(i in 1:length(v1_unique)){
  multiply_list[i] <- v1_unique[i]*v2_unique[i]
}
mutliply_matrix <- matrix(multiply_list, nrow = length(v1_unique), ncol = length(v2_unique))
#mutliply_matrix This matrix has too many columns for a pdf so we wont print it.
```

6-)By using one of your numeric variables, generate a new vector including the values greater than the median of this vector and name it as mynewvector.
```{r}
mynewvector <- data$cases[data$cases>median(data$cases)]
```

7-) Convert your data to a list, show the class of each member of your list
```{r}
data_list <- as.list(data)
lapply(data_list, FUN = typeof)
```

8-) Select your list elements by using their names.
```{r echo = T, results = 'hide'}
data_list$date
data_list$province
data_list$country
data_list$lat
data_list$long
data_list$cases
data_list$dumbeldors_army
#Because dataset is too long we wont print these.
```

9-)
```{r}
# Because that we have non numeric columns the max function returns the last value as the maximum. 
# Unlisting date variables is not good but for this questions sake we did it anyway...
for (i in 1:length(data_list)){
  list_names <- names(data_list)
  number <- i
  name <- names(data_list)[i]
  maxim <- max(unlist(data_list[list_names[i]]))
  cat("My", number,"variable name is" ,name , "and the greatest value for my vector is", maxim, "\n")
}
```

10-) Change one of your list element to NULL.
This means deleting the list so it wont show up in the head()
```{r}
data_list[["date"]] <- NULL
head(as.data.frame(data_list))
```
As seen above the "date" list is no longer there

11-)
```{r}
rm(list = ls(all.names = TRUE))
```




